The Exoplanet Orbit Database \textsc{II}: 2014 updates

### 2014-03-18 draft/ms.tex
Comments from the group meeting
Revisions and proofreading up to before Sec 3.

{\bf SEP} is the projected separation on the sky between the host star
and the planet in the unit of AU. For directly imaged planets, the
literatures usually report the projected separation and we report the
value accordingly.  If SEP is not directly measured but the semi-major
axis ($a$, A) is available, then SEP is set to A with its reference,
SEPREF, set to ``Set to A''. For the cases where only the projected
separation is given but A is not available (e.g., the directly imaged
planets), then A is set to SEP.

@@

We have added an entirely new set of fields for the secondary
eclipse. Previously, due to the limits of instrumentation, there were
not much available measured secondary eclipse depths. Since
\cite{Wright2011}, as many different surveys have been launched,
secondary eclipse depths at multiple bands are now
available. Therefore, we added this entire new set of fields since.

{\bf SE} flag indicates whether the system has detected secondary
eclipse in any of the two Micron All-Sky Survey (2MASS;
\citealt{Skrustskie2006}) $J$, $H$, and $K_s$, Kepler photometry band,
and 4 Spitzer IRAC bands. SE is a boolean and being true indicates the
system has at least one detected secondary eclipse.

@@

{\bf SET} is the epoch of secondary eclipse center in HJD.

@@

We provide the brightness of the host star measured in different
wavelengths. We report optical magnitudes ($V$ and $B-V$), 2MASS $J$,
$H$, and $K_s$ magnitudes and we added {\bf KP} since
\cite{Wright2011}, which is the stellar magnitude measured through the
Kepler bandpass.

%------------------------------------------------------------------------------
\subsection{Coordinates and Catalogs}\label{sec:coord}
We report the coordinates of the host star as well as the stellar ID
as designated by different catalogs.  We added {\bf DIST} since
\cite{Wright2011}, which is the distance of the host star in the unit
of pc. If only parallax (PAR) is given, we convert it to DIST and vice
versa. If the literature does not report DIST or PAR, then we obtain
PAR from the Hipparcos data set by \cite{van Leeuwen2009}.

We naively propagate the error in PAR to DIST.

@@

We now report uncertainties for a certain field X as XUPPER, XLOWER
and UX. XUPPER and XLOWER store the upper and lower 1$\sigma$
uncertainties, and they are different when the error bars are
asymmetric. UX contains the 1$\sigma$ uncertainty, and it equals to
$({\rm XUPPER+XLOWER})/2$ in the case of asymmetric error bars. Fields
that have XUPPER, XLOWER and UX are: all the orbital parameters except
for TREND and FREEZE\_ECC flags; all the transit parameters except for
TRANSIT flags; all the secondary eclipse fields except for SE flag;
and all the stellar properties except for STAR, SPECREF and BINARY
flag; and DIST and PAR.

We also report the upper limits (XUL) for planet mass (MSINI),
eccentricity (ECC), and the velocity semi-amplitude (K) when the
literatures report them. For example, the upper limits for ECC is
reported when the orbit is circular, and the upper limits for K is
reported when there is no radial velocity detection. If only upper
limits are given, we set the field to 0, the uncertainty to half of
the upper limit, and the upper limits to the upper limits. For
example, if the literature reports the upper limit for ECC, then we
put the value in ECCUL, set ECC to be 0, ECCUPPER to ECCUL, and UECC
to ECCUL/2. Since not all authors define the upper limits in the same
way (e.g. 1$\sigma$ or some fixed percentile), we encourage the
readers to refer to the literature for more information.

@@

The fields {\bf XREF} and {\bf XURL} store the peer-reviewed reference
and link to the publication for the field X.

Previously, we only reported general references (e.g. FIRSTREF,
FIRSTURL, ORBREF, and ORBURL), but now we report the references for
most of the fields.

RA, DEC, and PAR do not have references but they are from the
\textit{Hipparcos} by \cite{van Leeuwen2009}. $B-V$ (BMV) field does
not have a reference but the values are from the \textit{Hipparcos}
catalog by \cite{Perryman1997}. The fields J H and KS do not have
references as well but they are from the 2MASS
\citep{Skrutskie2006}. The KP field do not have reference but the
values are from the Exoplanet Archive \citep{Akeson2013}.

SHK and RHK are poorly maintained fields and they unreferenced at the
moment though we plan to include proper reference in the future. Most
of the values are from \cite{Butler2006}.

@@

We removed 2 fields.

{\bf SPSTAR} field previously reported the stellar type of the host
star but it is removed since it is not reliable.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Inclusion of the Kepler Planet Candidates and Other Exoplanets on Exoplanets.org}\label{sec:kepler}

>>>>

{\bf SEP} is the projected separation on the sky between the host star
and the planet in the unit of AU. For directly imaged planets, the
literatures usually report the projected separation and we report the
value accordingly.  If SEP is not directly measured but the semi-major
axis ($a$, A) is available, then SEP is set to A with its reference,
SEPREF, set to ``Set to A''.

@@

We have added an entirely new set of fields for the secondary
eclipse. Previously, due to the limits of instrumentation and limited
sample of exoplanets, there were not much secondary eclipse depth data
available. Since \cite{Wright2011}, as many different surveys have
been launched, more and more secondary eclipse depths at multiple
bands become available for more and more planets. Therefore, we added
this entire new set of fields.

{\bf SE} flag indicates whether the system has detected secondary
eclipse in any of the two Micron All-Sky Survey (2MASS;
\citealt{Skrutskie2006}) $J$, $H$, and $K_s$, Kepler photometry band,
and 4 Spitzer IRAC bands. SE is a boolean and SE $=$ 1 indicates the
system has at least one detected secondary eclipse.

@@

{\bf SET} is the epoch of secondary eclipse center (normally in HJD).

@@

We provide the brightness of the host star measured in different
wavelengths. We report optical magnitude and color ($V$ and $B-V$),
2MASS $J$, $H$, and $K_s$ magnitudes and we added {\bf KP} since
\cite{Wright2011}, which is the stellar magnitude measured through the
\kepler\ bandpass.

%------------------------------------------------------------------------------
\subsection{Coordinates and Catalogs}\label{sec:coord}

We report the coordinates of the host star as well as the host star's
ID as designated by different catalogs.  We added {\bf DIST} since
\cite{Wright2011}, which is the distance to the host star in the unit
of pc. If only parallax (PAR) is given, we calculate DIST based on PAR
and vice versa. If the literature does not report DIST or PAR, then we
obtain PAR from the Hipparcos dataset by \cite{van Leeuwen2009}. We
naively propagate the error in PAR to DIST and vice versa.

@@

We have changed the way of reporting uncertainties, especially
asymmetric error bars since \cite{Wright2011}. We now report
uncertainties for a certain field X as XUPPER, XLOWER and UX. XUPPER
and XLOWER store the upper and lower 1$\sigma$ uncertainties, and they
are different when the error bars are asymmetric. UX contains the
1$\sigma$ uncertainty, and it equals to $({\rm XUPPER+XLOWER})/2$ in
the case of asymmetric error bars. Fields that have XUPPER, XLOWER and
UX are: all the orbital parameters except for TREND and FREEZE\_ECC
flags; all the transit parameters except for TRANSIT flags; all the
secondary eclipse fields except for SE flag; and all the stellar
properties except for STAR, SPECREF and BINARY flag; and DIST and PAR.

We also report the upper limits (XUL) for planet minimum mass (MSINI),
eccentricity (ECC), and the radial velocity semi-amplitude (K) when
the literatures report them. For example, the upper limits for ECC is
reported when the orbit is consistent with a circular one, and the
upper limits for K is reported when there is only upper-limit radial
velocity detection. If only upper limits are given, we set the
parameter field X to 0, the uncertainty XU to half of the upper limit,
and the upper error bar XUPPER to the upper limits (same as XUL). For
example, if the literature reports the upper limit for ECC, which we
report in ECCUL, then we set ECC to be 0, ECCUPPER to ECCUL, and UECC
to ECCUL/2. Since not all authors define the upper limits in the same
way (e.g. 1$\sigma$ or some fixed percentile), we encourage the
readers to refer to the original references for more information.

@@

The fields {\bf XREF} and {\bf XURL} store the peer-reviewed reference
and link to the publication for the field X. Previously, we only
reported general references for certain sets of fields (e.g. FIRSTREF,
FIRSTURL, ORBREF, and ORBURL), but now we report the references for
most of the fields on an individual basis.

The following fields do not have associated REF or URL fields, and we
list their references here: RA, DEC, and PAR are from the
\textit{Hipparcos} by \cite{van Leeuwen2009}; the $B-V$ (BMV) values
are from the \textit{Hipparcos} catalog by \cite{Perryman1997};
stellar magnitudes J H and KS are from the 2MASS
\citep{Skrutskie2006}; the KP magnitudes are from the Exoplanet
Archive \citep{Akeson2013}.

SHK and RHK are poorly maintained fields, and they unreferenced at the
moment. We plan to include proper reference in the future. Most of the
SHK and RHK values are from \cite{Butler2006}.

@@

We removed 2 fields since \cite{Wright2011}:

{\bf SPSTAR} field previously reported the stellar type of the host
star, but it is removed since it is not reliable.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Inclusion of the Kepler Planet Candidates \\
  and Other Exoplanets on Exoplanets.org}\label{sec:kepler}
